---
title: "CaseStudy2Markdown"
author: "Jorge Olmos"
date: "12/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tm)
library(tidyr)
library(dplyr)
library(tidyverse)
library(e1071)
library(caret)
library(ggplot2)
library(kableExtra)
library(class)
library(modelr)
library(GGally)
library(corrplot)
library(readxl)
library(ggthemes)

theme <- theme_solarized_2(light=FALSE) + scale_colour_solarized('blue')


theme_set(theme_excel())

```

##Introduction

As a company that specializes in Talent Management we have been assigned in Identifying the top tree factors that lead to employee Attrition/Turnover.
Additionally we have been tasked with creating a model that predicts Attrition as well as model that predicts Monthly Income for the corporations employees.


#Reading and tidying datasets


## Reading in training data set

```{r, include=TRUE}
training_data = read.csv("CaseStudy2-data.csv", header=TRUE);
```


## Reading in test data set for attrition 

```{r, include=TRUE}
test_attrition_data = read.csv("CaseStudy2CompSet No Attrition.csv", header=TRUE)


```




##Reading Test data set for Monthly Income


```{r, include=TRUE}
test_salary_data = read_excel('CaseStudy2CompSet No Salary.xlsx')

```


##Removing unnecessary columns from training set and setting all categorial to be factors

```{r, include=TRUE}
training_data <- training_data %>% select(-one_of(c("Over18","StandardHours","EmployeeNumber","EmployeeCount")))
training_data$JobInvolvement <- as.factor(training_data$JobInvolvement)
training_data$JobLevel <- as.factor(training_data$JobLevel)
training_data$JobSatisfaction <- as.factor(training_data$JobSatisfaction)
training_data$PerformanceRating <- as.factor(training_data$PerformanceRating)
training_data$RelationshipSatisfaction <- as.factor(training_data$RelationshipSatisfaction)
training_data$StockOptionLevel <- as.factor(training_data$StockOptionLevel)
training_data$TrainingTimesLastYear <- as.factor(training_data$TrainingTimesLastYear)
training_data$WorkLifeBalance <- as.factor(training_data$WorkLifeBalance)
training_data$Education <- as.factor(training_data$Education)
training_data$EnvironmentSatisfaction <- as.factor(training_data$EnvironmentSatisfaction)


test_attrition_data <- test_attrition_data %>% select(-one_of(c("Over18","StandardHours","EmployeeNumber","EmployeeCount")))
test_attrition_data$JobInvolvement <- as.factor(test_attrition_data$JobInvolvement)
test_attrition_data$JobLevel <- as.factor(test_attrition_data$JobLevel)
test_attrition_data$JobSatisfaction <- as.factor(test_attrition_data$JobSatisfaction)
test_attrition_data$PerformanceRating <- as.factor(test_attrition_data$PerformanceRating)
test_attrition_data$RelationshipSatisfaction <- as.factor(test_attrition_data$RelationshipSatisfaction)
test_attrition_data$StockOptionLevel <- as.factor(test_attrition_data$StockOptionLevel)
test_attrition_data$TrainingTimesLastYear <- as.factor(test_attrition_data$TrainingTimesLastYear)
test_attrition_data$WorkLifeBalance <- as.factor(test_attrition_data$WorkLifeBalance)
test_attrition_data$Education <- as.factor(test_attrition_data$Education)
test_attrition_data$EnvironmentSatisfaction <- as.factor(test_attrition_data$EnvironmentSatisfaction)

test_salary_data <- test_salary_data %>% select(-one_of(c("Over18","StandardHours","EmployeeNumber","EmployeeCount")))
test_salary_data$JobInvolvement <- as.factor(test_salary_data$JobInvolvement)
test_salary_data$JobLevel <- as.factor(test_salary_data$JobLevel)
test_salary_data$JobSatisfaction <- as.factor(test_salary_data$JobSatisfaction)
test_salary_data$PerformanceRating <- as.factor(test_salary_data$PerformanceRating)
test_salary_data$RelationshipSatisfaction <- as.factor(test_salary_data$RelationshipSatisfaction)
test_salary_data$StockOptionLevel <- as.factor(test_salary_data$StockOptionLevel)
test_salary_data$TrainingTimesLastYear <- as.factor(test_salary_data$TrainingTimesLastYear)
test_salary_data$WorkLifeBalance <- as.factor(test_salary_data$WorkLifeBalance)
test_salary_data$Education <- as.factor(test_salary_data$Education)
test_salary_data$EnvironmentSatisfaction <- as.factor(test_salary_data$EnvironmentSatisfaction)



```


##Training data EDA

# Attrition By Department
```{r, include=TRUE}

grouped_by_department <- training_data %>% count(Department,Attrition)
reshape(grouped_by_department, idvar=c("Attrition","n"), timevar="Department", direction="wide")
spread(grouped_by_department, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum)  %>% ggplot(aes(Department,attrition_pct)) + geom_col()

```


## Attrition by Age

There seems to be a quadratic trend, there's a high level of attriction in late teens and early 20s. It levels off in the 30s, and starts picking back up in the 50s


```{r, include=TRUE}
grouped_by_age <- training_data %>% count(Age,Attrition)
spread(grouped_by_age, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(x = Age, y = attrition_pct)) + geom_point() +  geom_smooth(method = "loess") + labs(title = "Attrition vs. Age", x = "Age", y ="Attrition") 

```



##Attrition by JobSatisfaction

Seems to be a very strong correlation between JobSatisfaction and attrition rate, with the greater job satisfaction the better less the likelhood for attrition.


```{r, include=TRUE}
group_by_jobSatisfaction <- training_data %>% count(JobSatisfaction,Attrition)
spread(group_by_jobSatisfaction, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(x = JobSatisfaction, y = attrition_pct)) +  geom_point()   + labs(title = "Job Satisfaction vs. Attrition", x = "Job Satisfaction", y ="Attrition") 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



##Attrition by total working years

Similar to age it seems that there is less likelihood 

```{r, include=TRUE}
group_by_total_working_years <- training_data %>% count(TotalWorkingYears,Attrition)
spread(group_by_total_working_years, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(x = TotalWorkingYears, y = attrition_pct)) + geom_point()
```





##Attrition by Job Role
Sales representative appear to have a much higher attrition rate

```{r, include=TRUE}
group_by_job_role <- training_data %>% count(JobRole,Attrition)
spread(group_by_job_role, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(JobRole,attrition_pct)) + geom_col()
```


##Attrition by PercentSalaryHike
There's a very small correlation between percent salary hike and attrition

```{r, include=TRUE}
group_by_PercentSalaryHike <- training_data %>% count(PercentSalaryHike,Attrition)
spread(group_by_PercentSalaryHike, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(x = PercentSalaryHike, y = attrition_pct)) + geom_point()
```




##Attrition by hourly rate
Doesn't appear to be any real correlation between hourly rate and attrition
```{r, include=TRUE}
group_by_HourlyRate<- training_data %>% count(HourlyRate,Attrition)
spread(group_by_HourlyRate, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(x = HourlyRate, y = attrition_pct)) + geom_point()
```



##Attrition by OverTime
Working overtime appears to have a significant impact on attrition rate

```{r, include=TRUE}
group_by_OverTime<- training_data %>% count(OverTime,Attrition)
spread(group_by_OverTime, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(OverTime,attrition_pct)) + geom_col() + labs(title="Percentage of attrition by employess who take Over Time", x = "Over Time", y = "Attrition")
```


##Attrition by Monthly Income

```{r, include=TRUE}

group_by_MonthlyIncome<- na.omit(training_data) %>% count(MonthlyIncome,Attrition)
spread(group_by_MonthlyIncome, Attrition, n)  %>% mutate(sum = No+Yes) %>% mutate(attrition_pct = Yes/sum) %>% ggplot(aes(x = MonthlyIncome, y = attrition_pct)) + geom_point()

```

##Choosing to test Bayes models with factor that had the most impact on attrtion Age, Job Satisfaction, Totalworkinyears, Job Role, and Hourly Rate

Models is 86% accurate but low on specificity
```{r, include=TRUE}

set.seed(4)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age", "JobSatisfaction","TotalWorkingYears")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age", "JobSatisfaction","TotalWorkingYears")])))
CM



set.seed(4)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age", "JobSatisfaction","YearsWithCurrManager")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age", "JobSatisfaction","YearsWithCurrManager")])))
CM


set.seed(4)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","WorkLifeBalance","JobRole")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","WorkLifeBalance","JobRole")])))
CM


set.seed(4)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole")])))
CM


set.seed(7)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","JobSatisfaction")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","JobSatisfaction")])))
CM



AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)


for (seed in 1:100)
{

set.seed(seed)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","JobSatisfaction")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","JobSatisfaction")])))
CM
AccHolder[seed] = CM$overall[1]
SensHolder[seed] = CM$byClass[1]
SpecHolder[seed] = CM$byClass[2]

}

mean(AccHolder)
#Standard Error of the Mean
sd(AccHolder)/sqrt(100) 
mean(SensHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100) 
mean(SpecHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100)


set.seed(8)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","PercentSalaryHike")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","PercentSalaryHike")])))
CM

set.seed(6)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","JobSatisfaction","PercentSalaryHike")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","JobSatisfaction","PercentSalaryHike")])))
CM



AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)


for (seed in 1:100)
{

set.seed(seed)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","PercentSalaryHike")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","PercentSalaryHike")])))
CM
AccHolder[seed] = CM$overall[1]
SensHolder[seed] = CM$byClass[1]
SpecHolder[seed] = CM$byClass[2]

}

mean(AccHolder)
#Standard Error of the Mean
sd(AccHolder)/sqrt(100) 
mean(SensHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100) 
mean(SpecHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100)



AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)


for (seed in 1:100)
{

set.seed(seed)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","HourlyRate")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","HourlyRate")])))
AccHolder[seed] = CM$overall[1]
SensHolder[seed] = CM$byClass[1]
SpecHolder[seed] = CM$byClass[2]

}


mean(AccHolder)
#Standard Error of the Mean
sd(AccHolder)/sqrt(100) 
mean(SensHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100) 
mean(SpecHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100)

set.seed(12)

AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)


for (seed in 1:1000)
{

set.seed(seed)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","JobSatisfaction","OverTime")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","JobSatisfaction","OverTime")])))
CM
AccHolder[seed] = CM$overall[1]
SensHolder[seed] = CM$byClass[1]
SpecHolder[seed] = CM$byClass[2]

}

mean(AccHolder)
#Standard Error of the Mean
sd(AccHolder)/sqrt(100) 
mean(SensHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100) 
mean(SpecHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100)



```

##Best Bayes model included Age, JobRole, JobSatisfaction, and Overtime
Accuracy of 85%, sensitiviy of .85 and specificity of .65

```{r, include=TRUE}

AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)

for (seed in 1:100)
{

set.seed(seed)
trainIndices = sample(seq(1:length(training_data$Age)),round(.7*length(training_data$Age)))
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]
model = naiveBayes(trainEmployeeData[,c("Age","JobRole","JobSatisfaction","OverTime")],factor(trainEmployeeData$Attrition, labels = c("No", "Yes")))
CM = confusionMatrix(table(factor(testEmployeeData$Attrition, labels = c("No", "Yes")),predict(model,testEmployeeData[,c("Age","JobRole","JobSatisfaction","OverTime")])))
CM
AccHolder[seed] = CM$overall[1]
SensHolder[seed] = CM$byClass[1]
SpecHolder[seed] = CM$byClass[2]
}

mean(AccHolder)
#Standard Error of the Mean
sd(AccHolder)/sqrt(100) 
mean(SensHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100) 
mean(SpecHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100)

```

##Comparing against Knn Model
```{r, include=TRUE}


AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)

cleanEmployeeData <- na.omit(training_data)

splitPerc = .7
iterations = 100
numks = 60
masterAcc = matrix(nrow = iterations, ncol = numks)
  
for(j in 1:iterations)
{
set.seed(i)
accs = data.frame(accuracy = numeric(60), k = numeric(60))
trainIndices = sample(1:dim(cleanEmployeeData)[1],round(splitPerc * dim(cleanEmployeeData)[1]))
train = cleanEmployeeData[trainIndices,]
test = cleanEmployeeData[-trainIndices,]
for(i in 1:numks)
{
  classifications = knn(train[,c("JobSatisfaction","Age")],test[,c("JobSatisfaction","Age")],as.factor(train$Attrition), prob = TRUE, k = numks)
  table(as.factor(test$Attrition),classifications)
  CM = confusionMatrix(table(as.factor(test$Attrition),classifications))
  masterAcc[j,i] = CM$overall[1]
}

}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l")
which.max(MeanAcc)
max(MeanAcc)


AccHolder = numeric(100)
SensHolder = numeric(100)
SpecHolder = numeric(100)



for(i in 1:iterations){
  set.seed(i)
  trainIndices = sample(1:dim(cleanEmployeeData)[1],round(splitPerc * dim(cleanEmployeeData)[1]))
  train = cleanEmployeeData[trainIndices,]
  test = cleanEmployeeData[-trainIndices,]
  classifications = knn(train[,c("JobSatisfaction","Age")],test[,c("JobSatisfaction","Age")],as.factor(train$Attrition), prob = TRUE, k = 5)
  table(as.factor(test$Attrition),classifications)
  CM = confusionMatrix(table(as.factor(test$Attrition),classifications))
  AccHolder[i] = CM$overall[1]
  SensHolder[i] = CM$byClass[1]
  SpecHolder[i] = CM$byClass[2]
}


mean(AccHolder)
#Standard Error of the Mean
sd(AccHolder)/sqrt(100) 
mean(SensHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100) 
mean(SpecHolder)
#Standard Error of the Mean
sd(SensHolder)/sqrt(100)



```


##Classifying Attrition for Test Data

```{r, include=TRUE}

model = naiveBayes(training_data[,c("Age","JobRole","JobSatisfaction","OverTime")],factor(training_data$Attrition, labels = c("No", "Yes")))
test_attrition_data$Attrition = predict(model,test_attrition_data[,c("Age","JobRole","JobSatisfaction","OverTime")])
attrition_output <- test_attrition_data %>% select(ID,Attrition)
write.csv(attrition_output, file ="Case2PredictionsOlmosAttrition.csv", row.names = FALSE)

```


##EDA for imputing Monthly Income 

So far highest correlatoin is between Total working years and monthly income
Total working years has a .779 corr while years at company has .491 corr
JobLevel has a corr of .952
Age has a .485 correlation
Years since last promotion has a .316 correlation


```{r, include=TRUE}



# return correlation matrix of numerical values
training_data %>%
    keep(is.numeric) %>%
    tidyr::drop_na() %>%
    cor %>%
    corrplot("upper", addCoef.col = "white", number.digits = 2,
             number.cex = 0.5, method="square",
             order="hclust",
             tl.srt=45, tl.cex = 0.8)


training_data %>% select(HourlyRate, MonthlyRate,YearsInCurrentRole,TotalWorkingYears ,MonthlyIncome) %>% ggpairs()
training_data %>% select(PercentSalaryHike ,MonthlyIncome) %>% ggpairs()
training_data %>% select(YearsAtCompany ,MonthlyIncome) %>% ggpairs()
training_data %>% select(TotalWorkingYears ,MonthlyIncome) %>% ggpairs()
training_data %>% select(WorkLifeBalance ,MonthlyIncome) %>% ggpairs()
training_data %>% select(HourlyRate ,MonthlyIncome) %>% ggpairs()
training_data %>% select(JobLevel ,MonthlyIncome) %>% ggpairs()
training_data %>% select(DailyRate ,MonthlyIncome) %>% ggpairs()
training_data %>% select(Education ,MonthlyIncome) %>% ggpairs()
training_data %>% select(BusinessTravel ,MonthlyIncome) %>% ggpairs()
training_data %>% select(PercentSalaryHike ,MonthlyIncome) %>% ggpairs()
training_data %>% select(YearsSinceLastPromotion ,MonthlyIncome) %>% ggpairs()
training_data %>% select(JobRole ,MonthlyIncome) %>% ggpairs()
training_data %>% select(Age ,MonthlyIncome) %>% ggpairs()
training_data %>% select(StockOptionLevel ,MonthlyIncome) %>% ggpairs()
training_data %>% select(YearsWithCurrManager ,MonthlyIncome) %>% ggpairs()
training_data %>% select(NumCompaniesWorked ,MonthlyIncome) %>% ggpairs()
training_data %>% select(OverTime ,MonthlyIncome) %>% ggpairs()
training_data %>% select(StockOptionLevel ,MonthlyIncome) %>% ggpairs()
training_data %>% select(DistanceFromHome,MonthlyIncome ) %>% ggpairs()

```



##First Model for computing Monthly Incomes
First model using Joblevel and income has a rmse of 1410.878


```{r, include=TRUE}
training_data %>% ggplot(aes(x = JobLevel, y = MonthlyIncome)) + geom_point() + ggtitle("employeeData: JobLevel v. MonthlyIncome") + geom_smooth(method = "lm") 
training_data %>% ggplot(aes(x = JobRole, y = MonthlyIncome)) + geom_point() + ggtitle("employeeData: JobLevel v. MonthlyIncome") + geom_smooth(method = "lm")

fit = lm(MonthlyIncome~JobLevel, data = training_data)
summary(fit)
confint(fit)


generate_train_indices <- function(data,test_ratio,seed= as.numeric(Sys.time())){
    set.seed(seed)
    result <- list();
    trainInd = sample(seq(1,dim(data)[1],1),round(test_ratio*dim(data)[1]))
    return(trainInd);
}

#fit model 1

trainIndices = generate_train_indices(training_data,.7,4)
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]

summary(fit)
Model1_Preds = predict(fit, newdata = testEmployeeData)
MSPE = mean((testEmployeeData$MonthlyIncome - Model1_Preds)^2)
sqrt(MSPE)


```


##2nd Model ading TotalWorkingYears

Adding the totalworkingyears got a better error with 1365 


```{r, include=TRUE}

fit2 = lm(MonthlyIncome~JobLevel+TotalWorkingYears, data = training_data)
summary(fit2)
confint(fit2)


generate_train_indices <- function(data,test_ratio,seed= as.numeric(Sys.time())){
    set.seed(seed)
    result <- list();
    trainInd = sample(seq(1,dim(data)[1],1),round(test_ratio*dim(data)[1]))
    return(trainInd);
}

#fit model 1

trainIndices = generate_train_indices(training_data,.7,4)
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]

summary(fit2)
Model2_Preds = predict(fit2, newdata = testEmployeeData)

MSPE = mean((testEmployeeData$MonthlyIncome - Model2_Preds)^2)
sqrt(MSPE)

```
##3rd Model adding age as well

Found that adding the factors with most Correllations, that being JobLevel, Age, TotalWorkingYears gave the lowes RMSE of around 1200.


```{r}

fit3 = lm(MonthlyIncome~JobLevel+Age+TotalWorkingYears, data = training_data)
summary(fit3)
confint(fit3)

generate_train_indices <- function(data,test_ratio,seed= as.numeric(Sys.time())){
    set.seed(seed)
    result <- list();
    trainInd = sample(seq(1,dim(data)[1],1),round(test_ratio*dim(data)[1]))
    return(trainInd);
}

trainIndices = generate_train_indices(training_data,.7,4)
trainEmployeeData = training_data[trainIndices,]
testEmployeeData = training_data[-trainIndices,]

summary(fit3)
Model3_Preds = predict(fit3, newdata = testEmployeeData)
MSPE = mean((testEmployeeData$MonthlyIncome - Model3_Preds)^2)
sqrt(MSPE)







training_data %>% select(MonthlyIncome, JobLevel,Age,TotalWorkingYears ) %>% ggpairs(aes(color = JobLevel))

training_data %>% select(MonthlyIncome, JobLevel,Age,TotalWorkingYears ) %>% geom_point()

training_data %>% select(MonthlyIncome, JobLevel,Age,TotalWorkingYears)  %>% ggplot(aes(x = Age, y = MonthlyIncome, color = JobLevel)) + geom_point() 

training_data %>% select(MonthlyIncome, JobLevel,Age,TotalWorkingYears ,TotalWorkingYears)  %>% ggplot(aes(x = TotalWorkingYears, y = MonthlyIncome, color = JobLevel)) + geom_point() 









```

##Imputing the values for Test Set

```{r}


finale_monthly_salary_model = lm(MonthlyIncome~JobLevel+Age+TotalWorkingYears, data = training_data)
test_salary_data$MonthlyIncome = predict(finale_monthly_salary_model, newdata = test_salary_data)

finalSalaryOutput <- test_salary_data %>% select(ID,MonthlyIncome)

write.csv(finalSalaryOutput, file ="Case2PredictionsOlmosSalary.csv", row.names = FALSE)


```




